Spatial Analysis

### 2023-01-03 Scripts/spatial_analisis.Rmd
Get percentage of data included for each port

*License???.*

@@

ports_path <- my_path("G","AcrossBoundaries/Data/NOAA", name = "PalaciosJ - BSB, SFlounder, Scup by Port 1970-2020 - 2021.10.25.xlsx")

@@

>>>>

@@

ports_path <- here("Data/Raw/ACCSP/PalaciosJ - BSB, SFlounder, Scup by Port 1970-2020 - 2021.10.25.xlsx")

@@

# get percentage for revisions

overall_port_data %>% 
  group_by(species_name) %>% 
  summarise(total = sum(year_ton),
            n_tot = n()) %>% 
  left_join(top_ports) %>% 
  filter(tresh == "25th") %>% 
  group_by(species_name,total,n_tot) %>% 
  summarise(top_sum = sum(year_ton),
            n_top =n()
            ) %>% 
  mutate(round(top_sum/total,2),
         round(n_top/n_tot,2))
